1-methods-toys

### 2017-09-12 analysis/1-methods-toys.Rmd
added separate toy_params file and plotting

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_params <- list(
  waterfall=list(),
  scorpius=list(),
  slingshot=list(),
  gpfates=list(nfates=1),
  stemid=list(clustnr=10, bootnr=10, pdishuf=10),
  tscan=list(),
  embeddr=list(nn_pct = 2),
  celltree_gibbs=list(sd_filter = 0),
  celltree_maptpx=list(sd_filter = 0),
  celltree_vem=list(sd_filter = 0),
  scuba=list(),
  slicer = list(min_branch_len=50),
  monocle_ddrtree=list(),
  wishbone = list(branch=F),
  pseudogp = list(iter=100, initialise_from="principal_curve"),
  mpath = list(numcluster=6),
  random_linear=list()
)
method_names <- names(method_params)

@@

```{r}
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

@@

  factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, suppress_output = F)
  }
  )()
})
```

@@

scores %>% saveRDS("data/derived_data/toy_method_scores.rds")
```

@@

```{r}
scores %>%
  dplyr::select(-starts_with("time")) %>%
  gather(score_id, score, -method_name, -method_short_name, -task_id, -error, -warning) %>%
  ggplot() + geom_bar(aes(method_name, score, fill=score_id), stat="identity") + facet_wrap(~score_id) + coord_flip()
```

>>>>

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_params <- yaml::yaml.load_file("conf/toy_params.yml")$linear
method_names <- names(method_params)
method_names <- c("topslam")

@@

```{r}
# results <- PRISM::qsub_lapply(names(method_descriptions), function(method_name) {
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

@@

  factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, suppress_output = F)
  }
  )()
})
# }, qsub_environment = list2env(lst(method_descriptions, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1")))
```

@@

scores %>% saveRDS("results/toy_method_scores.rds")
```

@@

```{r fig.height=10, fig.width=10}
scores %>%
  dplyr::select(-starts_with("time")) %>%
  gather(score_id, score, -method_name, -method_short_name, -method_id, -task_id, -error, -warning, -model) %>%
  filter(score_id %in% c("errored", "correlation", "robbie_network_score", "mean_R_nx")) %>% 
  ggplot() + geom_bar(aes(method_name, score, fill=score_id), stat="identity") + facet_wrap(~score_id) + coord_flip()
```
